### 2019-09-20 2019_neurips_kr2ml/experiments.tex
Epoch 7 hard-na-hard

\begin{table}[htb]
\caption{Details of the Canonical and Hard variants of the COG dataset}
\centering
\begin{tabular}{lcccccc}
	\toprule
	Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
	& of   & memory & number of & of & of & of  \\
	& frames & duration & distractors & training set & validation set & test set \\
	\midrule
	Canonical & 4 & 3 & 1 & 10000320 & 500016? & 500016? \\	
	Hard  & 8 & 7 & 10 & 10000320 & 500016?  & 500016? \\
	\bottomrule	
\end{tabular}
\label{tab:cog_variants}
\end{table}

@@

\captionsetup[subfigure]{labelformat=empty}
\begin{figure}[htbp]
  \begin{center}
  Question: \textbf{Does color of u now equal the color of the latest circle?}
  \end{center}
  \vskip -0.4cm
  \null\hfill
  \begin{subfigure}{0.25\textwidth}
	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 1"}
	\caption{Frame: \textbf{1}\newline Ground Truth: \textbf{false}}
	\label{fig:frame-1}
  \end{subfigure}%
  \hfill
  \begin{subfigure}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 2"}
	\caption{Frame: \textbf{2}\newline Ground Truth: \textbf{false}}
	\label{fig:frame-2}
  \end{subfigure}%
  \hfill
  \begin{subfigure}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 3"}
	\caption{Frame: \textbf{3}\newline Ground Truth: \textbf{true}}
	\label{fig:frame-3}
  \end{subfigure}%
  \hfill
  \begin{subfigure}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/sample 2/Frame 4"}
	\caption{Frame: \textbf{4}\newline Ground Truth: \textbf{true}}
	\label{fig:frame-4}
  \end{subfigure}%
  \hfill\null
  \newline
  \centering
\caption{A sample from the COG dataset selected for the following analysis.} 
\label{fig:example}  
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 2 Step 1"}
	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 2.} 
	\label{fig:frame-2-step-1}
\end{figure}

@@

\begin{figure}[!h]
\centering
  \includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 2 Step 6"}
\caption{State of the SAM Cell after 6-th step of reasoning on Frame 2.} 
\label{fig:frame-2-step-6}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 4 Step 1"}
	\caption{State of SAMNet in a particular reasoning step} 
	\label{fig:frame-4-step-1}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.95\textwidth]{"../img/visualization/sample 2/Frame 4 Step 6"}
	\caption{State of SAMNet in a particular reasoning step} 
	\label{fig:frame-4-step-6}
\end{figure}

>>>>

\begin{table}[htb]
\caption{Details of the Canonical and Hard variants of the COG dataset}
\centering
\begin{tabular}{lcccccc}
	\toprule
	Variant    &  	number &  	maximum & maximum & size & size & size  \\ 
	& of   & memory & number of & of & of & of  \\
	& frames & duration & distractors & training set & validation set & test set \\
	\midrule
	Canonical & 4 & 3 & 1 & 10000320 & 500016? & 500016 \\	
	Hard  & 8 & 7 & 10 & 10000320 & 500016?  & 500016 \\
	\bottomrule	
\end{tabular}
\label{tab:cog_variants}
\end{table}

@@

\captionsetup[subfigure]{labelformat=empty}
\begin{figure}[htbp]
  \begin{center}
  Question: \textbf{Does color of u now equal the color of the latest circle?}
  \end{center}
  \vskip -0.4cm
  \null\hfill
  \begin{subfigure}{0.25\textwidth}
	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 1"}
	\caption{Frame: \textbf{1}\newline Ground Truth: \textbf{false}}
	\label{fig:frame-1}
  \end{subfigure}%
  \hfill
  \begin{subfigure}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2"}
	\caption{Frame: \textbf{2}\newline Ground Truth: \textbf{false}}
	\label{fig:frame-2}
  \end{subfigure}%
  \hfill
  \begin{subfigure}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 3"}
	\caption{Frame: \textbf{3}\newline Ground Truth: \textbf{true}}
	\label{fig:frame-3}
  \end{subfigure}%
  \hfill
  \begin{subfigure}{0.25\textwidth}
	\centering
	\includegraphics[width=0.9\linewidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4"}
	\caption{Frame: \textbf{4}\newline Ground Truth: \textbf{true}}
	\label{fig:frame-4}
  \end{subfigure}%
  \hfill\null
  \newline
  \centering
\caption{A sample from the COG dataset selected for the following analysis.} 
\label{fig:example}  
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 1"}
	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 2.} 
	\label{fig:frame-2-step-1}
\end{figure}

@@

\begin{figure}[!h]
\centering
  \includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 2 Step 6"}
\caption{State of the SAM Cell after 6-th step of reasoning on Frame 2.} 
\label{fig:frame-2-step-6}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 1"}
	\caption{State of the SAM Cell after 1-st step of reasoning on Frame 4.} 
	\label{fig:frame-4-step-1}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.95\textwidth]{"../img/visualization/experiment_run_20190917_022319/Frame 4 Step 6"}
	\caption{State of the SAM Cell after 6-th step of reasoning on Frame 4.} 
	\label{fig:frame-4-step-6}
\end{figure}
